Contextual Identity: A Framework for Usable Privacy

### 2012-10-12 paper.tex
minor text edits to definition section, standardize on lowercase p, use fullpage.sty to get under page limit

\usepackage{epsfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{ltxtable}
\usepackage{tabularx}
\usepackage{hhline}
\usepackage{color,colortbl}
\usepackage{url}
\usepackage{boxedminipage}
\usepackage{hyperref}
\usepackage{breakurl}
\usepackage{comment}
%\usepackage{fullpage}

@@

  We define a Contextual Identity $I = \{R,T,p\}$, where a user is performing tasks $T$ in view of or interaction with actors in $R$, while representing himself as identity $p$.
\end{definition}

A user may have multiple contextual identites $I$. These identities change over
time, as users form and dissolve relationships, and focus on different sets of
tasks. The user's goal is that the user can accomplish tasks in $T$, interact
with those in $R$ and claim to be $p$  while being able to predict and assert
control over as much of $I$ as possible.

@@

\begin{definition}
  A Contextual Identity Violation occurs when a user's contextual identity parameters $R,T,P$ are controlled by others.  When a user's tasks are shared with the wrong set $R$, the wrong projected identifier $p$ is employed, or a user is perceivied as undertaking a set of tasks $T$ they do not anticipate, a violation of the integrity of Contextual Identity occurs.
\end{definition}

@@

Another good partial solution is to prompt the user when they're about to link
multiple contextual identities through a federated login service. For example,
Persona is the suite of tools that implements the BrowserID protocol, and it
supports multiple email identifiers~\cite{browserid}. In this case, when the
user decides to register for a service using Persona, the task $T$ they are
performing is authentication, the relationships $R$ are ones they will engage
in when using the service, and $P$ is tied to the email identifier they use to
register for the service. Because we can categorize the type of service by URL
as \texttt{aboutprofile} does, Persona could prompt the user when they're about
to link the same email identifier to radically different contextual identities,
such as ones for dating and professional use.

>>>>

\usepackage{epsfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{ltxtable}
\usepackage{tabularx}
\usepackage{hhline}
\usepackage{color,colortbl}
\usepackage{url}
\usepackage{boxedminipage}
\usepackage{hyperref}
\usepackage{breakurl}
\usepackage{comment}
\usepackage{fullpage}

@@

  We define a Contextual Identity $I = \{R,T,p\}$, where a user performs tasks
$T$ in view of or interaction with actors in $R$, while representing identity
$p$.

\end{definition}

A user may have multiple contextual identites $\{I\}$. These identities change
over time, as users form and dissolve relationships, and focus on different
sets of tasks. The user's goal is to accomplish tasks in $T$,
interact with those in $R$ and claim to be $p$  while being able to predict and
assert control over as much of $I$ as possible.

@@

\begin{definition}
  A Contextual Identity Violation occurs when a user's contextual identity
parameters $R,T,p$ are controlled by others.  When a user's tasks are shared
with the wrong set $R$, the wrong projected identifier $p$ is employed, or a
user is perceivied as undertaking a set of tasks $T$ they do not anticipate, a
violation of the integrity of Contextual Identity occurs.

\end{definition}

@@

Another good partial solution is to prompt the user when they're about to link
multiple contextual identities through a federated login service. For example,
Persona is the suite of tools that implements the BrowserID protocol, and it
supports multiple email identifiers~\cite{browserid}. In this case, when the
user decides to register for a service using Persona, the task $T$ they are
performing is authentication, the relationships $R$ are ones they will engage
in when using the service, and $p$ is tied to the email identifier they use to
register for the service. Because we can categorize the type of service by URL
as \texttt{aboutprofile} does, Persona could prompt the user when they're about
to link the same email identifier to radically different contextual identities,
such as ones for dating and professional use.
